HydroPowerModels.jl: A Julia/JuMP Package for Hydrothermal Economic Dispatch Optimization

### 2022-02-20 paper/paper.tex
rm Plots and up JuMP, SDDP and PM

Use \texttt{create\_param} to create a set of problem parameters. For example, a 12-stage problem using the DC approximation can be specified as follows:
\begin{lstlisting}[language = Julia]
params = create_param( 
 stages      = 12, 
 stage_hours = 168.0,
 model_constructor_grid = DCPPowerModel,
 optimizer   = with_optimizer(GLPK.Optimizer))
\end{lstlisting}

>>>>

Use \texttt{create\_param} to create a set of problem parameters. For example, a 12-stage problem using the DC approximation can be specified as follows:
\begin{lstlisting}[language = Julia]
params = create_param( 
 stages      = 12, 
 stage_hours = 168.0,
 model_constructor_grid = DCPPowerModel,
 optimizer   = GLPK.Optimizer)
\end{lstlisting}
